---
title: 'Peer-graded Assignment: Getting and Cleaning Data Course Project'
author: "Helvio Markman"
date: "April 13, 2017"
output: html_document
---

##Reading inputs
```{r warning=FALSE, message=FALSE}
#train.x <- read.fwf(file = 'UCI HAR Dataset\\train\\x_train.txt',widths = rep(16,561))
train.x <- readRDS('train_x.rda')
head(train.x[,1:5],5)
#test.x <- read.fwf(file = 'UCI HAR Dataset\\test\\x_test.txt',widths = rep(16,561))
test.x <- readRDS('test_x.rda')
head(test.x[,1:5],5)
```

##Reading outputs
```{r warning=FALSE, message=FALSE}
train.y <- read.table(file = 'UCI HAR Dataset\\train\\y_train.txt')
str(train.y)
test.y <- read.table(file = 'UCI HAR Dataset\\test\\y_test.txt')
str(test.y)
```

### Reading features
```{r warning=FALSE, message=FALSE}
features <- read.table(file = 'UCI HAR Dataset\\features.txt',sep=' ')
str(features)
```
### Reading Activity Labes
```{r warning=FALSE, message=FALSE}
activity_labels <- read.table(file = 'UCI HAR Dataset\\activity_labels.txt',sep=' ')
names(activity_labels) = c('id','activity')
head(activity_labels)
```
### Reading Subject
```{r warning=FALSE, message=FALSE}
train.subject <- read.table(file = 'UCI HAR Dataset\\train\\subject_train.txt')
str(train.subject)
test.subject <- read.table(file = 'UCI HAR Dataset\\test\\subject_test.txt')
str(test.subject)
```

###Label inputs and extracting means only (Question 4 and 2)
```{r, warning=FALSE,message=FALSE}
names(train.x)=features[,2]

names(test.x)=features[,2]

means_coluns = grepl("mean",names(train.x))
train.x.means <- train.x[,means_coluns]
test.x.means <- test.x[,means_coluns]
head(train.x.means[,1:5])
head(test.x.means[,1:5])
```

### Join subject and outputs for train and Activities label (Question 3)
```{r warning=FALSE, message=FALSE}
train.tidy <- train.x.means
train.tidy[,'act_id'] <- train.y
train.tidy[,'subject'] <- train.subject
train.tidy <- merge(train.tidy,activity_labels,by.x='act_id',by.y='id',all=TRUE)

str(train.tidy)
```

### Join subject and outputs for test and Activities label (Question 3)
```{r warning=FALSE, message=FALSE}
test.tidy <- test.x.means
test.tidy[,'act_id'] <- test.y
test.tidy[,'subject'] <- test.subject
test.tidy <- merge(test.tidy,activity_labels,by.x='act_id',by.y='id',all=TRUE)

str(test.tidy)
```

###Merge Train and test data sets (question 1)
```{r warning=FALSE,message=FALSE}
tidy <- rbind(train.tidy,test.tidy)
str(tidy)
```
####tidy has `r nrow(tidy)` rows and `r ncol(tidy)` columns

####Summary of tidy means of numeric columns group by subejct and activity(Question 5)
```{r, warning=FALSE, message=FALSE}
hide_cols <- (names(tidy) != 'activity')
tidy.summary <- aggregate(tidy[,hide_cols],by= list(tidy$act_id, tidy$subject),mean)
tidy.summary <- merge(tidy.summary,activity_labels,by.x='act_id',by.y='id')
ts_order <- order(tidy.summary$subject)

tidy.summary[ts_order[1:5],c('activity','subject','tBodyAcc-mean()-Y','tBodyAcc-mean()-Z','tGravityAcc-mean()-X')]

```

###Sample of Tidy data summary

