---
title: "README"
author: "Helvio Markman"
date: "April 14, 2017"
output: html_document
---
# Getting_and_Cleaning_data_Project
Peer-graded Assignment: Getting and Cleaning Data Course Project

```{r, warning=FALSE, message=FALSE}
tidy <- read.csv('tidy.csv',header = TRUE, sep = ';')
tidy.summary <- read.csv('tidy_summary.csv',header = TRUE, sep = ';')
```
###Human Activity Recognition Using Smartphones Data Set 

####Data Set Information:
The experiments have been carried out with a group of 30 volunteers within an age bracket of 19-48 years. Each person performed six activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING) wearing a smartphone (Samsung Galaxy S II) on the waist. Using its embedded accelerometer and gyroscope, we captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz. The experiments have been video-recorded to label the data manually. The obtained dataset has been randomly partitioned into two sets, where 70% of the volunteers was selected for generating the training data and 30% the test data. 

data website: 
'https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip'

tidy dataset is the combination of train and test datasets with every mean feature.
it has `r nrow(tidy)` observations and `r ncol(tidy)` columns.
Active is a factor variable with the folling levels `r levels(tidy$activity)`.

##Variables in tidy data set ("tidy.csv", with ";" as separetor)
```{r, warning=FALSE, message=FALSE} 
str(tidy)
```

##Variable from Tidy.Summary dataset (tidy_summary.csv, with ";" as separetor)
```{r, warning=FALSE, message=FALSE}
str(tidy.summary)
```

####Relevant Papers:

Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra and Jorge L. Reyes-Ortiz. Human Activity Recognition on Smartphones using a Multiclass Hardware-Friendly Support Vector Machine. International Workshop of Ambient Assisted Living (IWAAL 2012). Vitoria-Gasteiz, Spain. Dec 2012 

Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra, Jorge L. Reyes-Ortiz. Energy Efficient Smartphone-Based Activity Recognition using Fixed-Point Arithmetic. Journal of Universal Computer Science. Special Issue in Ambient Assisted Living: Home Care. Volume 19, Issue 9. May 2013

Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra and Jorge L. Reyes-Ortiz. Human Activity Recognition on Smartphones using a Multiclass Hardware-Friendly Support Vector Machine. 4th International Workshop of Ambient Assited Living, IWAAL 2012, Vitoria-Gasteiz, Spain, December 3-5, 2012. Proceedings. Lecture Notes in Computer Science 2012, pp 216-223. 

Jorge Luis Reyes-Ortiz, Alessandro Ghio, Xavier Parra-Llanas, Davide Anguita, Joan Cabestany, Andreu Català. Human Activity and Motion Disorder Recognition: Towards Smarter Interactive Cognitive Environments. 21th European Symposium on Artificial Neural Networks, Computational Intelligence and Machine Learning, ESANN 2013. Bruges, Belgium 24-26 April 2013.

